On the Minimum Core Mass for Giant Planet Formation through Kelvin-Helmholtz Contraction

### 2013-02-21 tex/draft/draft2.tex
added new paper figs
- taller figs, removed delad info
- added analytic curves
updated plots

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Pd_effect.pdf}
%\vspace{-0.5in}
\caption{Disk pressure effect on growth time. Gas accretion is faster for higher pressures.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Td_effect.pdf}
%\vspace{-0.5in}
\caption{Disk temperature effect on growth time. Gas accretion is faster for lower temperatures.}
\end{figure}

@@

Moreover, the critical core mass increases for a lower mean molecular weight and a smaller adiabatic gradient. This is consistent with the results derived in section \ref{Mct}. The critical core mass is strongly dependent on the mean molecular weight $\mu$, but only weakly depended on the adiabatic index $\gamma$ (or $\delad$).

>>>>

%\begin{figure}[h]
%\centering
%\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Pd_effect.pdf}
%%\vspace{-0.5in}
%\caption{Disk pressure effect on growth time. Gas accretion is faster for higher pressures.}
%\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/TdPd_effect.pdf}
%\vspace{-0.5in}
\caption{Disk temperature effect on growth time. Gas accretion is faster for lower temperatures.}
\end{figure}

@@

Moreover, the critical core mass increases for a lower mean molecular weight and a smaller adiabatic index. This is consistent with the results derived in section \ref{Mct}. The critical core mass is strongly dependent on the mean molecular weight $\mu$, but only weakly depended on the adiabatic index $\gamma$ (or $\delad$).
